# dsincubator

Transcript database for the [ds-incubator YouTube playlist](https://youtube.com/playlist?list=PLvgdJdJDL-APbB315sB3Lv_2VP2g0ioFO&si=LOZAcXpa1L7JlVvc): `data/metadata.csv` + `transcripts/<id>_<title>.md` (OKF v0.2 format), linked by `id` — then transformed into an OKF v0.2 LLM wiki **[`dsincubator/`](dsincubator/index.md)** per `planning_manifest.json`. Flags: `--from`/`--to` for directories, `--csv`/`--manifest` for files, `--wiki-name`/`--wiki-tag` for identity.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
#| include: false
library(readr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
library(fs)
library(stringr)
library(purrr)
library(tibble)
library(jsonlite)
```

## Structure

```
data/metadata.csv            # derived table, 151 videos
metadata/<id>.json           # raw per-video dump (yt-dlp)
transcripts/<id>_<title>.md  # OKF v0.2 transcript (YAML frontmatter + body)
transcripts/manifest.tsv     # id | status | file | lang
planning_manifest.json       # wiki plan: 59 topic pages across 13 categories
dsincubator/            # OKF v0.2 wiki → see Wiki below  (wiki/ subdir is canonical: dsincubator/wiki/index.md)
dsincubator/sources/    # 151 distilled sources (one per transcript)
dsincubator/topics/     # 59 topic pages (each an OKF concept with type)
dsincubator/index.md    # wiki root (okf_version 0.2 §12)  — also at dsincubator/wiki/index.md
dsincubator/log.md      # wiki history (§9)
bin/fetch-metadata           # raw dumps + derive CSV
bin/fetch-transcripts        # fetch captions (json3)
bin/convert-transcripts      # json3 -> txt/tsv/md (OKF v0.2)
bin/distill-sources          # transcript .md + CSV → sources/source_<id>_<slug>.md
bin/cluster-topics           # auto-cluster sources → planning_manifest.json
bin/generate-topics          # manifest + sources → topics/{category}/{topic}.md
bin/assemble-wiki            # generate index.md, indexes, log.md, references/  # alias: assemble-bundle shim
bin/build-wiki               # orchestrator: runs full pipeline
requirements.txt             # Python deps for clustering (numpy, scipy, sklearn, hdbscan)
```

## Fetch

### Quick start (any playlist)

```sh
# Build a wiki for any public playlist in one command
./bin/build-wiki --playlist "https://youtube.com/playlist?list=..." --wiki-name dslab --wiki-tag ds-lab --to ./dslab --count 3
```

### Individual steps

```sh
# Metadata: test then full (append new by default)
./bin/fetch-metadata --limit 2        # smoke test (first 2 playlist entries)
./bin/fetch-metadata                  # fetch missing dumps, derive data/metadata.csv
./bin/fetch-metadata --refresh        # re-fetch all dumps, drop removed rows

# Transcripts: test then full
./bin/fetch-transcripts --count 3     # test
./bin/fetch-transcripts               # 151 videos (one *-orig json3 per video)
# add --cookies-from-browser chrome whenever output contains "Sign in to confirm you're not a bot"
# --force re-fetches existing

# Convert json3 → readable formats
./bin/convert-transcripts --format md --count 3   # test
./bin/convert-transcripts --format md              # all 151 → transcripts/<id>_<slug>.md (OKF v0.2)
./bin/convert-transcripts --format all             # txt + tsv + md

# Distill sources (extract key_topics + restructure body)
./bin/distill-sources --csv data/metadata.csv --from transcripts --to dsincubator/sources --wiki-tag ds-incubator

# Auto-cluster sources into topics
./bin/cluster-topics --from dsincubator/sources --to planning_manifest.json --wiki-name dsincubator

# Generate topic pages
./bin/generate-topics --manifest planning_manifest.json --from dsincubator/sources --to dsincubator/topics

# Assemble wiki (index.md, indexes, log.md, references/)
./bin/assemble-wiki --from dsincubator --manifest planning_manifest.json --wiki-name dsincubator --wiki-tag ds-incubator
```

> **Note on `sources/` summaries:** `bin/distill-sources` as shipped is **deterministic and offline** — it scaffolds frontmatter from `data/metadata.csv` + `transcripts/*.md` and fills `key_topics` via word-frequency. The 151 `dsincubator/sources/` distilled via LLM (Extraction Prompt v2 at `AGENTS.md:178`) are not reproduced by `build-wiki`; the generalized bundles (`dslab`, `dshangout`) currently contain placeholder summaries. Replace the placeholder with an LLM pass (`--llm` flag) to get Summary + Key Concepts + Code Snippets per Extraction Prompt v2.

Run directly via `bin/build-wiki` (no task runner):

```sh
./bin/build-wiki --playlist "https://www.youtube.com/playlist?list=PL..." --wiki-name dslab --wiki-tag ds-lab --to ./dslab --count 3
```

### Example metadata

```{r}
dsi <- readr::read_csv("data/metadata.csv", show_col_types = FALSE)
dsi |> glimpse()
```

```{r}
dsi |> select(upload_date_iso, title, url)
```

```{r}
transcript_files <- dir_ls("transcripts", regexp = "\\.md$") |>
  tibble(path = _) |>
  mutate(filename = path_file(path))

transcript_ids <- transcript_files |>
  mutate(id = purrr::map_chr(filename, ~ dsi$id[startsWith(.x, paste0(dsi$id, "_"))][1])) |>
  select(id, transcript_path = path)

joined <- dsi |>
  left_join(transcript_ids, by = "id")

joined |>
  select(id, title, transcript_path)
```

### Example transcript

```{r}
fs::dir_ls("transcripts/", regexp = "[.]md")[[5]] |> readLines(n = 30) |> writeLines()
```

## Wiki

👉 **Start here: [`dsincubator/index.md`](dsincubator/index.md)** — bundle root (OKF v0.2, 151 sources → 59 topics). Indexes: [`dsincubator/topics/index.md`](dsincubator/topics/index.md) (§8) with entry [`dsincubator/topics/concepts-overview.md`](dsincubator/topics/concepts-overview.md), [`dsincubator/sources/index.md`](dsincubator/sources/index.md). History: [`dsincubator/log.md`](dsincubator/log.md) (§9). References: [`dsincubator/references/`](dsincubator/references/).

Build pipeline:
1. `./bin/build-wiki` — one-command orchestrator (fetch → transcripts → convert → distill → cluster → topics → wiki)
2. Or step-by-step: `bin/distill-sources` → `bin/cluster-topics` → `bin/generate-topics` → `bin/assemble-wiki` (alias `assemble-bundle` still works)

### Generalized wiki — `dslab` example

Any public playlist can produce a wiki. Tested with **dslab** (`PL9HYL-VRX0oSeWeMEGQt0id7adYQXebhT`, 27 videos) → [`dslab/wiki/index.md`](dslab/wiki/index.md) (§12) + [`dslab/README.md`](dslab/README.md). Flags: `--from`/`--to` (dirs), `--csv`/`--manifest` (files), `--wiki-name`/`--wiki-tag` (identity).

```sh
./bin/build-wiki --playlist "https://www.youtube.com/playlist?list=PL9HYL-VRX0oSeWeMEGQt0id7adYQXebhT" --wiki-name dslab --wiki-tag ds-lab --to ./dslab --count 3  # quick test
./bin/build-wiki --playlist "https://www.youtube.com/playlist?list=PL9HYL-VRX0oSeWeMEGQt0id7adYQXebhT" --wiki-name dslab --wiki-tag ds-lab --to ./dslab          # full (27)
```

Outputs: `dslab/metadata.csv`, `dslab/transcripts/<id>_<slug>.md` (body `00:08: text` per `tStartMs`, deterministic — no LLM; `lang` prefers `en-orig`/`es-orig`), `dslab/sources/`, `dslab/topics/`, `dslab/index.md` (§12), `dslab/log.md` (§9).

Full pipeline: 151 `sources/` distilled per Extraction Prompt v2 (frozen frontmatter, quote-to-name, anchored `key_topics`) → `bin/cluster-topics` uses TF-IDF + HDBSCAN auto-clustering with silhouette evaluation → aggregation populates `planning_manifest.json` `source_files[]` → 59 `topics/` with cross-links (§6) and `Attested Computation` for pipelines (§10) → bundle assembly (`index.md` §8, `topics/index.md` §8, `sources/index.md` §8, `log.md` §9, `references/` §6.3). Status 2026-09-08: `status: draft` until human `verified` (§5.2).

### Example topics

```{r}
manifest <- jsonlite::read_json("planning_manifest.json")
topic_paths <- purrr::map_chr(manifest$topics, "topic_filename")

tibble(path = topic_paths) |>
  mutate(category = stringr::str_extract(path, "(?<=topics/)[^/]+")) |>
  filter(path != "topics/concepts-overview.md") |>
  count(category, name = "topics") |>
  arrange(dplyr::desc(topics))
```

### Example source

```{r}
fs::dir_ls("dsincubator/sources", regexp = "source_.*\\.md$")[[1]] |> readLines(n = 40) |> writeLines()
```

### Example topic

```{r}
fs::dir_ls("dsincubator/topics", regexp = "\\.md$", recurse = TRUE)[[2]] |> readLines(n = 40) |> writeLines()
```

### Search the wiki with qmd (complements LLM)

[`qmd`](https://github.com/tobi/qmd) complements brute-force LLM (`cat`/`rg`) — local hybrid search (BM25 + vector + LLM rerank) without loading the bundle. Install: `npm install -g @tobilu/qmd` or `bun install -g @tobilu/qmd` / `npx @tobilu/qmd` — <https://github.com/tobi/qmd>. Collection `dsincubator` is indexed; after changes: `qmd update && qmd embed -c dsincubator`.

```{bash}
qmd search "docker" -c dsincubator -n 2 | head -n 20
```

```{bash}
qmd query "how to handle merge conflicts git" -c dsincubator -n 2
```

Use `qmd query` for prose/questions, `qmd search`/`rg` for exact symbols (`tar_make`, `expect_snapshot`), then `qmd get` to pull context. See `qmd --help` and `rg --help`.

See other [tips and tricks](https://gist.github.com/karpathy/442a6bf555914893e9891c11519de94f#tips-and-tricks) (thanks `@karpathy`).
