# dsincubator

Transcript database for the [ds-incubator YouTube playlist](https://youtube.com/playlist?list=PLvgdJdJDL-APbB315sB3Lv_2VP2g0ioFO&si=LOZAcXpa1L7JlVvc): `data/metadata.csv` + `transcripts/<id>_<title>.md` (OKF format), linked by `id`.

## Repository Structure

```
data/metadata.csv            # derived table, 151 videos
transcripts/<id>_<title>.md  # OKF transcript (YAML frontmatter + body)
transcripts/manifest.tsv     # id | status | file | lang
bin/fetch-metadata           # raw dumps + derive CSV
bin/fetch-transcripts        # fetch captions
bin/convert-transcripts      # json3 -> txt/tsv/md
```

## Metadata Overview

```{r}
library(readr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)

dsi <- readr::read_csv("data/metadata.csv", show_col_types = FALSE)
dsi |> glimpse()
```

## Sample Metadata

```{r}
dsi |> select(upload_date_iso, title, url) |> head(10)
```

## Transcript Join

Lists `.md` transcripts from the filesystem, extracts the video `id`, and left-joins with `data/metadata.csv`.

```{r}
library(fs)
library(dplyr)
library(stringr)
library(readr)

transcript_files <- dir_ls("transcripts", regexp = "\\.md$") |>
  tibble(path = _) |>
  mutate(filename = path_file(path))

transcript_ids <- transcript_files |>
  mutate(id = sapply(filename, function(f) {
    dsi$id[startsWith(f, paste0(dsi$id, "_"))][1]
  })) |>
  select(id, transcript_path = path)

joined <- dsi |>
  left_join(transcript_ids, by = "id")

joined |>
  select(id, title, transcript_path) |>
  head(10)
```

## Join Summary

```{r}
cat("Rows in metadata:", nrow(dsi), "\n")
cat("Matched transcripts:", sum(!is.na(joined$transcript_path)), "\n")
```

## Sample Transcript

```{r}
first_path <- joined$transcript_path[1]
cat("File:", first_path, "\n\n")
readLines(first_path, n = 30) |> paste(collapse = "\n") |> cat()
```

## Fetch / Refresh Commands

```sh
# Transcripts
./bin/fetch-transcripts --count 3   # test
./bin/fetch-transcripts               # full

# Metadata
./bin/fetch-metadata --limit 2      # test
./bin/fetch-metadata              # append new
./bin/fetch-metadata --refresh    # rewrite all

# Convert to readable formats (txt, tsv, md)
./bin/convert-transcripts --format md --count 3
./bin/convert-transcripts --format md
```
