# dsincubator

Transcript database for the [ds-incubator YouTube playlist](https://youtube.com/playlist?list=PLvgdJdJDL-APbB315sB3Lv_2VP2g0ioFO&si=LOZAcXpa1L7JlVvc): `data/metadata.csv` + `transcripts/<id>_<title>.md` (OKF format), linked by `id`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
#| include: false
library(readr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
library(fs)
library(stringr)
library(purrr)
library(tibble)
library(jsonlite)
```

## Structure

```
data/metadata.csv            # derived table, 151 videos
transcripts/<id>_<title>.md  # OKF transcript (YAML frontmatter + body)
transcripts/manifest.tsv     # id | status | file | lang
planning_manifest.json       # wiki plan: 44 topic pages across 13 categories
dsincubator_wiki/sources/    # distilled wiki sources (3 pilots; 148 pending)
bin/fetch-metadata           # raw dumps + derive CSV
bin/fetch-transcripts        # fetch captions
bin/convert-transcripts      # json3 -> txt/tsv/md
```

## Overview

```{r}
dsi <- readr::read_csv("data/metadata.csv", show_col_types = FALSE)
dsi |> glimpse()
```

```{r}
dsi |> select(upload_date_iso, title, url)
```

```{r}
transcript_files <- dir_ls("transcripts", regexp = "\\.md$") |>
  tibble(path = _) |>
  mutate(filename = path_file(path))

transcript_ids <- transcript_files |>
  mutate(id = purrr::map_chr(filename, ~ dsi$id[startsWith(.x, paste0(dsi$id, "_"))][1])) |>
  select(id, transcript_path = path)

joined <- dsi |>
  left_join(transcript_ids, by = "id")

joined |>
  select(id, title, transcript_path)
```

## Example transcript

```{r}
fs::dir_ls("transcripts/", regexp = "[.]md")[[5]] |> readLines(n = 30) |> writeLines()
```

## Wiki (OKF LLM bundle)

The 151 transcripts feed an OKF v0.2 knowledge bundle (`dsincubator_wiki/`), planned in `planning_manifest.json` with distilled `sources/` (one per transcript) aggregated into topic pages.

```{r}
manifest <- jsonlite::read_json("planning_manifest.json")

tibble(
  bundle = manifest$bundle_name,
  transcripts = manifest$total_transcripts_processed,
  topics = manifest$total_planned_topics
)
```

```{r}
topic_paths <- purrr::map_chr(manifest$topics, "topic_filename")

tibble(path = topic_paths) |>
  mutate(category = stringr::str_extract(path, "(?<=topics/)[^/]+")) |>
  filter(path != "topics/concepts-overview.md") |>
  count(category, name = "topics") |>
  arrange(dplyr::desc(topics))
```

```{r}
wiki_sources <- dir_ls("dsincubator_wiki/sources", regexp = "\\.md$") |>
  tibble(source_path = _)

tibble(
  sources_done = nrow(wiki_sources),
  sources_pending = manifest$total_transcripts_processed - nrow(wiki_sources)
)
```

```{r}
wiki_sources |> select(source_path)
```

## Commands

```sh
# Transcripts
./bin/fetch-transcripts --count 3   # test
./bin/fetch-transcripts               # full

# Metadata
./bin/fetch-metadata --limit 2      # test
./bin/fetch-metadata              # append new
./bin/fetch-metadata --refresh    # rewrite all

# Convert to readable formats (txt, tsv, md)
./bin/convert-transcripts --format md --count 3
./bin/convert-transcripts --format md
```
