# dsincubator

Transcript database for the [ds-incubator YouTube playlist](https://youtube.com/playlist?list=PLvgdJdJDL-APbB315sB3Lv_2VP2g0ioFO&si=LOZAcXpa1L7JlVvc): `data/metadata.csv` + `transcripts/<id>_<title>.md` (OKF v0.2 format), linked by `id` — then transformed into an OKF v0.2 LLM wiki bundle **[`dsincubator/`](dsincubator/index.md)** per `planning_manifest.json`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
#| include: false
library(readr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
library(fs)
library(stringr)
library(purrr)
library(tibble)
library(jsonlite)
```

## Structure

```
data/metadata.csv            # derived table, 151 videos
metadata/<id>.json           # raw per-video dump (yt-dlp)
transcripts/<id>_<title>.md  # OKF v0.2 transcript (YAML frontmatter + body)
transcripts/manifest.tsv     # id | status | file | lang
planning_manifest.json       # wiki plan: 59 topic pages across 13 categories
dsincubator/            # OKF v0.2 wiki bundle → see Wiki below
dsincubator/sources/    # 151 distilled sources (one per transcript)
dsincubator/topics/     # 59 topic pages (each an OKF concept with type)
dsincubator/index.md    # bundle root (okf_version 0.2 §12)
dsincubator/log.md      # bundle history (§9)
bin/fetch-metadata           # raw dumps + derive CSV
bin/fetch-transcripts        # fetch captions (json3)
bin/convert-transcripts      # json3 -> txt/tsv/md (OKF v0.2)
```

## Fetch

```sh
# Metadata: test then full (append new by default)
./bin/fetch-metadata --limit 2        # smoke test (first 2 playlist entries)
./bin/fetch-metadata                  # fetch missing dumps, derive data/metadata.csv
./bin/fetch-metadata --refresh        # re-fetch all dumps, drop removed rows

# Transcripts: test then full
./bin/fetch-transcripts --count 3     # test
./bin/fetch-transcripts               # 151 videos (one *-orig json3 per video)
# add --cookies-from-browser chrome whenever output contains "Sign in to confirm you're not a bot"
# --force re-fetches existing

# Convert json3 → readable formats
./bin/convert-transcripts --format md --count 3   # test
./bin/convert-transcripts --format md              # all 151 → transcripts/<id>_<slug>.md (OKF v0.2)
./bin/convert-transcripts --format all             # txt + tsv + md
```

### Example metadata

```{r}
dsi <- readr::read_csv("data/metadata.csv", show_col_types = FALSE)
dsi |> glimpse()
```

```{r}
dsi |> select(upload_date_iso, title, url)
```

```{r}
transcript_files <- dir_ls("transcripts", regexp = "\\.md$") |>
  tibble(path = _) |>
  mutate(filename = path_file(path))

transcript_ids <- transcript_files |>
  mutate(id = purrr::map_chr(filename, ~ dsi$id[startsWith(.x, paste0(dsi$id, "_"))][1])) |>
  select(id, transcript_path = path)

joined <- dsi |>
  left_join(transcript_ids, by = "id")

joined |>
  select(id, title, transcript_path)
```

### Example transcript

```{r}
fs::dir_ls("transcripts/", regexp = "[.]md")[[5]] |> readLines(n = 30) |> writeLines()
```

## Wiki

👉 **Start here: [`dsincubator/index.md`](dsincubator/index.md)** — bundle root (OKF v0.2, 151 sources → 59 topics). Indexes: [`dsincubator/topics/index.md`](dsincubator/topics/index.md) (§8) with entry [`dsincubator/topics/concepts-overview.md`](dsincubator/topics/concepts-overview.md), [`dsincubator/sources/index.md`](dsincubator/sources/index.md). History: [`dsincubator/log.md`](dsincubator/log.md) (§9). References: [`dsincubator/references/`](dsincubator/references/).

Build: 151 `sources/` distilled per Extraction Prompt v2 (frozen frontmatter, quote-to-name, anchored `key_topics`) → aggregation populates `planning_manifest.json` `source_files[]` → 59 `topics/` with cross-links (§6) and `Attested Computation` for pipelines (§10) → bundle assembly (`index.md` §8, `topics/index.md` §8, `sources/index.md` §8, `log.md` §9, `references/` §6.3). Status 2026-09-08: `status: draft` until human `verified` (§5.2).

### Example topics

```{r}
manifest <- jsonlite::read_json("planning_manifest.json")
topic_paths <- purrr::map_chr(manifest$topics, "topic_filename")

tibble(path = topic_paths) |>
  mutate(category = stringr::str_extract(path, "(?<=topics/)[^/]+")) |>
  filter(path != "topics/concepts-overview.md") |>
  count(category, name = "topics") |>
  arrange(dplyr::desc(topics))
```

### Example source

```{r}
fs::dir_ls("dsincubator/sources", regexp = "source_.*\\.md$")[[1]] |> readLines(n = 40) |> writeLines()
```

### Example topic

```{r}
fs::dir_ls("dsincubator/topics", regexp = "\\.md$", recurse = TRUE)[[2]] |> readLines(n = 40) |> writeLines()
```

### Search the wiki with qmd (complements LLM)

[`qmd`](https://github.com/tobi/qmd) complements brute-force LLM (`cat`/`rg`) — local hybrid search (BM25 + vector + LLM rerank) without loading the bundle. Install: `npm install -g @tobilu/qmd` or `bun install -g @tobilu/qmd` / `npx @tobilu/qmd` — <https://github.com/tobi/qmd>. Collection `dsincubator` is indexed; after changes: `qmd update && qmd embed -c dsincubator`.

```{bash}
qmd search "docker" -c dsincubator -n 2 | head -n 20
```

```{bash}
qmd query "how to handle merge conflicts git" -c dsincubator -n 2
```

Use `qmd query` for prose/questions, `qmd search`/`rg` for exact symbols (`tar_make`, `expect_snapshot`), then `qmd get` to pull context. See `qmd --help` and `rg --help`.

The bundle is plain markdown — browse it locally with [Obsidian](https://obsidian.md) (open `dsincubator/` as vault, use graph view, backlinks, and [Dataview](https://github.com/blacksmithgu/obsidian-dataview) for frontmatter queries) or any markdown editor. `qmd` already indexes it for the LLM; humans get the same files in Obsidian.

See other [tips and tricks](https://gist.github.com/karpathy/442a6bf555914893e9891c11519de94f#tips-and-tricks).

---

Thanks https://gist.github.com/karpathy/ for the [post](https://gist.github.com/karpathy/442a6bf555914893e9891c11519de94f) that brought my attention to LLM wikis.
