# dsincubator

Transcript database for the [ds-incubator YouTube playlist](https://youtube.com/playlist?list=PLvgdJdJDL-APbB315sB3Lv_2VP2g0ioFO&si=LOZAcXpa1L7JlVvc): `data/metadata.csv` + `transcripts/<id>_<title>.md` (OKF v0.2 format), linked by `id` — then transformed into an OKF v0.2 LLM wiki bundle **[`dsincubator_wiki/`](dsincubator_wiki/index.md)** per `planning_manifest.json`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
#| include: false
library(readr, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
library(fs)
library(stringr)
library(purrr)
library(tibble)
library(jsonlite)
```

## Structure

```
data/metadata.csv            # derived table, 151 videos
metadata/<id>.json           # raw per-video dump (yt-dlp)
transcripts/<id>_<title>.md  # OKF v0.2 transcript (YAML frontmatter + body)
transcripts/manifest.tsv     # id | status | file | lang
planning_manifest.json       # wiki plan: 59 topic pages across 13 categories
dsincubator_wiki/            # OKF v0.2 wiki bundle → see Wiki below
dsincubator_wiki/sources/    # 151 distilled sources (one per transcript)
dsincubator_wiki/topics/     # 59 topic pages (each an OKF concept with type)
dsincubator_wiki/index.md    # bundle root (okf_version 0.2 §12)
dsincubator_wiki/log.md      # bundle history (§9)
bin/fetch-metadata           # raw dumps + derive CSV
bin/fetch-transcripts        # fetch captions (json3)
bin/convert-transcripts      # json3 -> txt/tsv/md (OKF v0.2)
```

## 1. Fetch

Raw-first pipeline: `yt-dlp` dumps to `metadata/` and `transcripts/`, then CSV derived.

```sh
# Metadata: test then full (append new by default)
./bin/fetch-metadata --limit 2        # smoke test (first 2 playlist entries)
./bin/fetch-metadata                  # fetch missing dumps, derive data/metadata.csv
./bin/fetch-metadata --refresh        # re-fetch all dumps, drop removed rows

# Transcripts: test then full
./bin/fetch-transcripts --count 3     # test
./bin/fetch-transcripts               # 151 videos (one *-orig json3 per video)
# add --cookies-from-browser chrome whenever output contains "Sign in to confirm you're not a bot"
# --force re-fetches existing
```

## 2. Example: What was fetched

### Metadata + transcripts (joined by `id`)

```{r}
dsi <- readr::read_csv("data/metadata.csv", show_col_types = FALSE)
dsi |> glimpse()
```

```{r}
dsi |> select(upload_date_iso, title, url)
```

```{r}
transcript_files <- dir_ls("transcripts", regexp = "\\.md$") |>
  tibble(path = _) |>
  mutate(filename = path_file(path))

transcript_ids <- transcript_files |>
  mutate(id = purrr::map_chr(filename, ~ dsi$id[startsWith(.x, paste0(dsi$id, "_"))][1])) |>
  select(id, transcript_path = path)

joined <- dsi |>
  left_join(transcript_ids, by = "id")

joined |>
  select(id, title, transcript_path)
```

### Example transcript (5th file, first 30 lines)

```{r}
fs::dir_ls("transcripts/", regexp = "[.]md")[[5]] |> readLines(n = 30) |> writeLines()
```

## 3. Process

Convert captions to readable OKF v0.2 and distill into the wiki bundle.

```sh
# Convert json3 → readable formats (txt + tsv + md)
./bin/convert-transcripts --format md --count 3   # test
./bin/convert-transcripts --format md              # all 151 → transcripts/<id>_<slug>.md (OKF v0.2)
./bin/convert-transcripts --format all             # txt + tsv + md

# Wiki build (done 2026-09-08: 151 sources → 59 topics → bundle)
# 1. sources/ : distill each transcript → dsincubator_wiki/sources/source_<id>_<slug>.md
#    per Extraction Prompt v2 (frozen frontmatter, quote-to-name, anchored key_topics)
# 2. aggregation : read all sources → populate planning_manifest.json source_files[]
# 3. topics/  : 59 pages with cross-links (§6), Attested Computation for pipelines (§10)
# 4. bundle assembly : index.md (§8), topics/index.md (§8), sources/index.md (§8), log.md (§9), references/ (§6.3)
```

## 4. Example: What was processed — the wiki

👉 **Start here: [`dsincubator_wiki/index.md`](dsincubator_wiki/index.md)** — bundle root (OKF v0.2, 151 sources → 59 topics). Directory indexes: [`dsincubator_wiki/topics/index.md`](dsincubator_wiki/topics/index.md) (§8) with entry point [`dsincubator_wiki/topics/concepts-overview.md`](dsincubator_wiki/topics/concepts-overview.md), and [`dsincubator_wiki/sources/index.md`](dsincubator_wiki/sources/index.md). History: [`dsincubator_wiki/log.md`](dsincubator_wiki/log.md) (§9). External attesters: [`dsincubator_wiki/references/`](dsincubator_wiki/references/).

Status 2026-09-08: **151/151 sources** and **59/59 topics** complete (type §4.1, sources credibility §5.1, actor `agent:okf-wiki-builder/1.0` §7, cross-links §6, `Attested Computation` for `targets`/`drake` §10); `planning_manifest.json` `source_files[]` populated; bundle indexes and `log.md` present; `status: draft` until human `verified` (§5.2).

```{r}
manifest <- jsonlite::read_json("planning_manifest.json")

tibble(
  bundle = manifest$bundle_name,
  okf_version = manifest$okf_version,
  transcripts = manifest$total_transcripts_processed,
  topics = length(manifest$topics)
)
```

```{r}
topic_paths <- purrr::map_chr(manifest$topics, "topic_filename")

tibble(path = topic_paths) |>
  mutate(category = stringr::str_extract(path, "(?<=topics/)[^/]+")) |>
  filter(path != "topics/concepts-overview.md") |>
  count(category, name = "topics") |>
  arrange(dplyr::desc(topics))
```

### Distilled sources (live)

```{r}
wiki_sources <- dir_ls("dsincubator_wiki/sources", regexp = "source_.*\\.md$") |>
  tibble(source_path = _)

tibble(
  sources_done = nrow(wiki_sources),
  sources_pending = manifest$total_transcripts_processed - nrow(wiki_sources)
)
```

```{r}
wiki_sources |> head(10) |> select(source_path)
```

### Example distilled source (first pilot, first 40 lines)

```{r}
fs::dir_ls("dsincubator_wiki/sources", regexp = "source_.*\\.md$")[[1]] |> readLines(n = 40) |> writeLines()
```

### Example topic (first 40 lines)

```{r}
fs::dir_ls("dsincubator_wiki/topics", regexp = "\\.md$", recurse = TRUE)[[2]] |> readLines(n = 40) |> writeLines()
```
